---
title: "p8105_hw5_jsg2145"
author: "Jared Garfinkel"
date: "11/3/2019"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

##Problem 1

```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

```{r}
iris_with_missing <- iris_with_missing %>% 
  janitor::clean_names()
```

```{r, example 2, results = "hide"}
iris_with_missing %>% 
  mutate(sepal_length = 
           replace_na(sepal_length, 
                      round(mean(sepal_length, na.rm = TRUE), digits = 1)))
```

```{r, example char, results = "hide"}
iris_with_missing %>% 
  mutate(species = 
           replace_na(species, "virginica"))
```

```{r}
df <- iris_with_missing
```

```{r, for loop char}
output_c = vector("list", length = 150)

for (i in 1:150) {
  output_c[[i]] = replace_na(pull(iris_with_missing, species)[[i]], "virginica")
}
```

```{r}
output = vector("list", length = 150)

for (i in 1:150) {
  output[[i]] = if_else(is.na(pull(iris_with_missing, sepal_length)[[i]]),
                        round(mean(pull(iris_with_missing, sepal_length), na.rm = TRUE),
                              digits = 1), 
                        pull(iris_with_missing, sepal_length)[[i]])
}
```

```{r}
output = vector("list", length = 150)

for (i in 1:150) {
  output[[i]] = replace(pull(iris_with_missing, sepal_length)[[i]], 
                        is.na(pull(iris_with_missing, sepal_length)[[i]]), 
                        round(mean(pull(iris_with_missing, sepal_length), na.rm = TRUE), digits = 1))
}
```

```{r, for loop}
iris_df <- iris_with_missing %>% 
  select(-species)

output = vector("list", length = 150)

for (i in 1:150) {
  output[[i]] = replace_na(pull(iris_df, sepal_length)[[i]], 
                           round(mean(pull(iris_df, sepal_length), 
                                      na.rm = TRUE), 
                                 digits = 1))
}
```


```{r, general function}
impute_dat = function(df = iris_with_missing, x){
  if (is.character(x)) {
    df %>% 
      mutate(x = 
               replace_na(x,
                          "virginica")) %>% 
    pull(x)
  } else
  df %>% 
    mutate(x = 
    replace_na(x, round(
      mean(x, na.rm = TRUE),
      digits = 1))) %>% 
  pull(x)
}
```

```{r, for loop over function, results = "hide"}
output_f = vector("list", length = 5)

for (i in 1:5) {
  output_f[[i]] = impute_dat(x = df[[i]])
}

output_f
```

```{r, results = "hide"}
fix_df <- map_dfr(iris_with_missing, ~impute_dat(x = .x))

fix_df
```


## Problem 2

```{r, example prob 2, message = FALSE}
data <- read_csv("./hw5_data/data/con_01.csv")
```


```{r, dataframe}
titles <- tibble(
  file_names = list.files("./hw5_data/data"),
)
```

```{r, message = FALSE}
output_t = vector("list", length = 20)
path = vector("list", length = 20)

for (i in 1:20) {
  path[[i]] = str_c("./hw5_data/data", pull(titles, file_names)[[i]], sep = "/")
  output_t[[i]] = read_csv(path[[i]])
}
```


```{r, read_data}
read_data <- function(df = titles, x) {
  path = str_c("./hw5_data/data", x, sep = "/")
  data = read_csv(path)
}
```

```{r, message = FALSE}
output_ts = vector("list", length = 20)

for (i in 1:20) {
  output_ts[[i]] = read_data(x = pull(titles, file_names)[[i]])
}
```

```{r, message = FALSE}
exp_df <- titles %>% 
  mutate(
    data = map(.x = pull(titles, file_names), ~read_data(x = .x))) %>% 
  unnest()
```

```{r}
exp_tidy <- exp_df %>% 
  pivot_longer(cols = week_1:week_8, names_to = "week") %>% 
  mutate(file_names =
           str_replace(file_names, ".csv", ""),
         file_names = 
           str_replace_all(file_names, c("con_" = "control ", "exp_" = "experimental ")))
```

```{r}
exp_tidy %>% 
  group_by(file_names) %>% 
  mutate(week = as_factor(week),
         week = as.numeric(week),
         labels = ifelse(str_detect(file_names, "^con"), "control", "experimental")) %>% 
  ggplot(aes(x = week, y = value, color = file_names)) +
  geom_point() +
  geom_smooth(se = FALSE) +
  facet_grid(~labels) +
  theme(legend.position = "none")
```

It appears that the measured variable stayed the same over the study period 

in the control group and went up over time for the experimental group.

## Problem 3

```{r}
sim_df <- tibble(
  n = 30,
  x_i1 = rnorm(30),
  B_0 = 2,
  s2 = 50,
  B_1 = 0
)
```

```{r}
sim_regression = function(B_0 = 2, B_1 = 0, s2 = 50) {
  sim_df <- tibble(
    x = rnorm(30, mean = 0, sd = 1),
    y = B_0 + B_1 * x + rnorm(30, 0, s2)
  )
  sim_fit = lm(y ~ x, data = sim_df) %>% 
    broom::tidy()

  tibble(
    p = pull(sim_fit, p.value)[2],
    B_1hat = pull(sim_fit, estimate)[2]
  )
}
```
  
```{r}
output = vector("list", length = 100)

for (i in 1:100) {
  output[[i]] = sim_regression() %>% 
    bind_rows()
}
```

```{r}
B_1list = list("B_10" = 0, 
              "B_11" = 1, 
              "B_12" = 2, 
              "B_13" = 3,
              "B_14" = 4,
              "B_15" = 5,
              "B_16" = 6)

output = vector("list", length = 7)

for (i in 1:7) {
  output[[i]] = rerun(100, sim_regression(B_1 = B_1list[[i]])) %>% 
    bind_rows()
}
```

```{r}
output_df = map(B_1list, ~rerun(10000, sim_regression(B_1 = .x)))
```

```{r}
output_tib = bind_rows(list(output_df)) %>% 
  pivot_longer(cols = B_10:B_16, names_to = "B_1hat") %>% 
  unnest() %>% 
  rename(B_1 = B_1hat1) %>% 
  group_by(B_1hat) %>%
  filter(p < 0.05) %>% 
  summarize(count = n()) %>% 
  mutate(prop = count/10000,
         B_1hat = as.factor(B_1hat),
         B_1hat = as.numeric(B_1hat),
         B_1hat = B_1hat - 1)
```

```{r}
output_tib %>% 
  ggplot(aes(x = B_1hat, y = prop)) +
  geom_point() +
  geom_smooth(se = FALSE)
```

```{r}
output_unnest = bind_rows(list(output_df)) %>% 
  pivot_longer(cols = B_10:B_16, names_to = "B_1hat") %>% 
  unnest() %>% 
  rename(B_1 = B_1hat1) %>%
  mutate(B_1hat = as.factor(B_1hat),
         B_1hat = as.numeric(B_1hat),
         B_1hat = B_1hat - 1)
```


```{r}
p1 <- output_unnest %>% 
  group_by(B_1hat) %>% 
  summarize(
    mean_est = mean(B_1)
  )
```

```{r}
p2 <- output_unnest %>% 
  filter(p < 0.05) %>% 
  group_by(B_1hat) %>% 
  summarize(
    mean_est = mean(B_1)
  )
```

```{r}
ggplot(p1, aes(x = B_1hat, y = mean_est)) +
  geom_point(color = "blue") +
  geom_smooth(se = FALSE) +
  geom_point(data = p2, color = "red") +
  geom_smooth(data = p2, se = FALSE, color = "red")
```

Typically, the sample average of $\hat{\beta_1}$ across tests for which the null is rejected

is not expected to approximate the true value of $\beta_1$. However, it can approximate the true value

if there are a similar number of estimates greater than and less than the true value. 

The linear model function tests whether the estimated paramaters match the actual value of 

the parameter given a random sample of x. So, a rejection of the null indicates that the estimated

paramater does not match the true parameter.